\begin{thebibliography}{99}
\bibitem{OIJ}O~K~Takai, I~C~Italiano e J~E~Ferreira,\\
  \mbox{}\hfill \textsl{Introdução a Banco de Dados, cp.10 - Data Warehouse, Uma visão geral}\\
  \mbox{}\hfill\texttt{\url{http://www.ime.usp.br/~jef/apostila.pdf}}

\bibitem{dw} C~Adamson, M~Venerable. Data Warehouse Design Solutions, John Wiley \& Sons, 1998.

\bibitem{dw2} M~Golfarelli, D~Maio, S~Rizzi. “Conceptual Design of Data Warehouses from E/R
 Schemes”, Proceedings of the Hawaii International Conference on System Sciences,
  Kona, Hawaii, USA, 1998  

\bibitem{VR}Vincent Rainardi, Building a Data Warehouse: With Examples in SQL Server, \textsl{Chapter 8: Populating the Data Warehouse},
\\ 
\mbox{}\hfill\texttt{\url{http://books.google.com.br/books?id=KEW\_AUD6GegC}}

\bibitem{navat} E. R. Elmasri and S. Navathe and. Fundamentals of Database Systems. Editora
Addison Wesley Pub, 2001.

\bibitem{rama} R. Ramakrishnan and J. Gehrke. Database Management Systems. 3a. Edição.
 McGraw-Hill, 2003.

\bibitem{RTF}Roy Fielding, Architectural Styles and the Design of Network-based Software Architectures, 2000
\\ 
\mbox{}\hfill\small{\texttt{\url{http://www.ics.uci.edu/~fielding/pubs/dissertation/top.htm}}}
\normalsize{}

\bibitem{SMPP}Snehal Mumbaikar, Puja Padiya. Web Services Based On SOAP and REST Principles, 
International Journal of Scientific and Research Publications, Volume 3, Issue 5, May 2013,
\textsl{ISSN 2250-3153}
\mbox{}\hfill\texttt{\url{http://www.ijsrp.org/research-paper-0513/ijsrp-p17115.pdf}}

\bibitem{LS}Leonard Richardson e Sam Ruby, RESTful Web Services (O'Relly), 2008
\\ 
\mbox{}\hfill\texttt{\url{http://books.google.com.br/books?id=XUaErakHsoAC}}

\bibitem{BB}Bill Burke, RESTful Java with JAX-RS (O'Relly), 2010
\\ 
\mbox{}\hfill\texttt{\url{http://books.google.com.br/books?id=\_jQtCL5\_vAcC}}

\bibitem{plai} Shriram Krishnamurthi,\\ Programming Languages: Application and Interpretation (Second Edition), 2012, cp. 15.2.7 - Type Soundness

\bibitem{plai_obj} Shriram Krishnamurthi,\\ Programming Languages: Application and Interpretation (Second Edition), 2012, cp.10 - Objects

\bibitem{ajax} Jesse James Garrett, Ajax: A New Approach to Web Applications, 2005
\\ 
\mbox{}\hfill\texttt{\url{https://web.archive.org/web/20080702075113/http://www.adaptivepath.com/ideas/essays/archives/000385.php}}

\bibitem{craw} Vladislav Shkapenyuk and Torsten Suel, Design and implementation of a high-performance
distributed web crawler, Polytechnic University Brooklyn, NY 2002
\mbox{}\hfill\texttt{\url{http://cis.poly.edu/~suel/papers/crawl.pdf}}


\bibitem{h-index} J.E. Hirsch, An index to quantify an individual's scientific research output, 2005\\
\mbox{}\hfill\texttt{\url{http://arxiv.org/abs/physics/0508025}}

\bibitem{sclt} J. P. Mena-Chalco e R. M. Cesar-Jr. scriptLattes: An open-source knowledge extraction system from the Lattes platform. Journal of the Brazilian Computer Society, vol. 15, n. 4, páginas 31--39, 2009.\\
\mbox{}\hfill\texttt{\url{http://scriptlattes.sourceforge.net/}}


\end{thebibliography}
